\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{geometry}
\geometry{
a4paper,
left=20mm,
right=20mm,
top=20mm,
bottom=20mm
}
\pagenumbering{gobble}
\begin{document}
\noindent

\begin{tabularx}{\textwidth}{X r}
    \huge{\textbf{Anthony Catterwell}} 
    & Email: anthony.catterwell@gmail.com \\
    & Mobile: +44 7572019279 \\
    & Github: https://www.github.com/MadCommy \\
\end{tabularx}

\hline
\section*{Personal projects and experience}
\begin{itemize}
    \item \textbf{Compiler}:
        for a subset of C to MIPS.
        (Java, MIPS) (Ongoing)
    \item \textbf{Battleships}: game with single-player
        and multi-player support.  
        (Python)
    \item \textbf{Twitter-bot detector}:
        co-created program to identify 
        bot-accounts on Twitter at Hack the Burgh 2018.
        (Python, Twitter API)
    \item \textbf{Login monitor}:
        service which remotely logs user
        logins to university computers. (Python)
    \item \textbf{Search program}:
        indexes and searches university students and 
        staff given their roles.  (Python)
    \item \textbf{Micro-bit controllers}:
        motion-sensitive Micro-bit controllers for a 
        game of Pong at Hack the Burgh. Won ARM prize.
        (Python, Micro-bit API)
    \item \textbf{Spellchecker}:
        runs in constant time. (C)
    \item \textbf{Programming internship}:
        at Centara Grande Hotels' head office.
        Contributed to the back-end of their staff website involving user-account management.
        C#, SQL (July 2016)
\end{itemize}

\hline
\section*{Relevant skills}
\begin{tabularx}{\textwidth}{X r}
    Java, Python & \textit{Very competent} \\
    Kotlin, Haskell, C, C#, SQL, XML & \textit{Good understanding} \\
    Linux and *-nix command line & \textit{Very competent, daily use} \\
    Git & \textit{Quite competent, regular use} \\
\end{tabularx}

\hline
\section*{Education}
\begin{tabularx}{\textwidth}{X r}
    \textbf{University of Edinburgh} & Edinburgh, UK \\
    \textit{Computer Science and Mathematics BSc. (Hons)} expected 1st & Sept 2016 -- \\
    \begin{tabular}{l r}
        Year 1: $84\%$ average (120 credits) \\
        Year 2: $82\%$ average (160 credits) \\
    \end{tabular} & \\

    \textbf{Bangkok Patana School} & Bangkok, Thailand \\
    \textit{International Baccalaureate} & August 2014 -- June 2016\\
    \begin{tabular}{l}
        Higher level: Mathematics, Physics, Chemistry \\
        Standard level: Economics, English, Thai \\
    \end{tabular}
\end{tabularx}

\hline
\section*{Clubs, Societies, and Extracurriculars}
\begin{tabularx}{\textwidth}{X r}
    University of Edinburgh Game Development Society member & 2017 -- \\
    University of Edinburgh Computing Society member & 2016 -- \\
    University of Edinburgh Mathematics Society member & 2016 --\\
    DipABRSM Piano Performance & 2014
\end{tabularx}

\end{document}
