\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{centernot}
\usepackage{hyperref}
\usepackage{eufrak}
\usepackage{graphicx}

\geometry{a4paper, left=20mm, right=20mm, top=20mm, bottom=20mm}
\pagenumbering{gobble}

\begin{document}

\noindent

\begin{center}
    \begin{tabular}{c}
        \Huge{\textsc{Anthony Catterwell}} \\
        \scriptsize{anthony.catterwell@gmail.com \quad +447572019279} \\
    \end{tabular}
\end{center}

\midrule

\textsc{About me}

\begin{tabularx}{\textwidth}{l X}
    \textbf{Professional interests} & Cloud architectures, distributed systems,
        machine learning, data mining, web-development. \\
    \textbf{Legal status} & British and Thai dual citizen. \\
\end{tabularx}

\midrule

\textsc{Education}

\begin{tabularx}{\textwidth}{X r}
    \textbf{The University of Edinburgh} & Edinburgh, UK \\
        BSc. (Hons), Computer Science and Mathematics, 1:1 (expected) & 2016 ---
        2020 (expected) \\
    \begin{tabular}{l l l l}
        Year 1         & Year 2         & Year 3         & Year 4 \\
        $84\%$ average & $82\%$ average & $79\%$ average & ongoing \\
    \end{tabular} & \\
    \textbf{Bangkok Patana School} & Bangkok, Thailand \\
    IB Diploma (38/45)             & 2014 --- 2016 \\
\end{tabularx}

\midrule

\textsc{Employment}

\begin{tabularx}{\textwidth}{X r}
    \textbf{Software Development Engineering Intern} & Jun 2019 --- Sep 2019 \\
    Amazon Europe Core S\`arl & Luxembourg City, Luxembourg \\
\end{tabularx}
\begin{tabularx}{\textwidth}{X}
    \begin{itemize}
        \item Implemented, tested, and deployed component of high-throughput,
            high-availability data-retrieval service to enable the fetching of data from
            additional sources in AWS.\@
        \item Designed, implemented, tested, and deployed front-end web UI and
            associated back-end REST service to enable self-service bulk data submission
            by internal customers.
        \item Created metrics and dashboards for measuring and monitoring performance
            and data quality.
    \end{itemize}
\end{tabularx}

\midrule

\textsc{Selected projects}
\begin{itemize}
    \item \textbf{C Compiler}:
        Built a compiler for a subset of C to MIPS-Assembly. (Java, MIPS.)
    \item \textbf{Predictive classifier of exam performance}:
        Designed and developed a performant machine-learning model to predict performance
        of students in an online exam given logged data recorded earlier in the same exam.
        This constitutes a leading submission to the NAEP Data Mining Competition 2019.
        (Python, Pandas, Scikit-learn, XGBoost.)
    \item \textbf{Android App \emph{Coinz}}:
        Designed and implemented location-based coin collection-game. (Java, Android,
        Firebase, Mapbox, Material-UI.)
    \item \textbf{Select components of a DBMS}:
        Implemented B-tree record manager, and heap file of a simple database management
        system. (C++, Minibase.)
    % \item \textbf{LLVM Compiler Pass}:
    %     Wrote dead-code elimination pass in LLVM.\@ \textit{C++, LLVM}
    % \item \textbf{RL agents for OpenAI Gym}:
    %     Designed and implemented several reinforcement-learning agents (DQN, REINFORCE,
    %     N-Step Actor Critic) for solving OpenAI's CartPole and LunarLander environments.
    %     \textit{Python, PyTorch}
    % \item \textbf{AI for multiplayer game}:
    %     Designed and implemented an AI for a tank in a multiplayer game. GreatUniHack
    %     2018. \textit{Python}
    % \item \textbf{TUI game \emph{Battleships}}:
    %     Designed and implemented battleships game with single- and multi-player (over TCP)
    %     modes. \textit{Python}
    % \item \textbf{Street Maintenance App}:
    %     Implemented back-end of server-less pothole-reporting app. HackUPC 2018.
    %     \textit{Java, Android, AWS Lambda, AWS DynamoDB}
    % \item \textbf{Login monitor}:
    %     Designed and implemented service to remotely record logins to networked university
    %     computers. \textit{Python}
    % \item \textbf{Staff search-engine}:
    %     Created to search university staff and students given their roles. \textit{Python}
    % \item \textbf{Twitter-bot detector}:
    %     Co-created program to identify bot-accounts on Twitter. Hack the Burgh 2018.
    %     \textit{Python, Twitter API}
    % \item \textbf{Micro-bit game-controllers}:
    %     Designed and implemented motion-sensitive micro-bit game-controllers. Hack the
    %     Burgh 2017.  Won ARM prize. \textit{Python, Micro-bit API}
    % \item \textbf{Spellchecker}:
    %     Wrote constant-time spellchecker. \textit{C} (June 2015)
\end{itemize}

\midrule

\textsc{Technologies}

\begin{tabularx}{\textwidth}{X r}
    Java, Python, Linux, Git, SQL, Guice, Mockito, AWS (S3), Vim, \LaTeX{}
    & \textit{***} \\\\

    PyTorch, C++, MapReduce (Hadoop), TypeScript, Angular, Unix shell scripts, Pandas,
    Scikit-learn, REST, Firebase, Mapbox, Android, Maple, AWS (DynamoDB, Lambda)
    & \textit{**} \\\\

    Hibernate, Spring, Haskell, MIPS assembly, LLVM, MATLAB, R, AWS (Data Pipeline,
    Redshift, RDS)
    & \textit{*} \\\\
\end{tabularx}
\begin{scriptsize}
\begin{tabular}{l l}
    *** & Extensive use in multiple major projects. \\
    **  & Substantial use in at least one major project. \\
    *   & Good familiarity through use in at least one smaller project or minor use in a
    major project.
\end{tabular}
\end{scriptsize}

\end{document}
